---
title: "Working group/symposium on capture-recapture models and social networks"
description: "Introduction to demographic (capture-recapture) models in Nimble"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```



### Requirements

+ Install [`R`](https://cloud.r-project.org/) and [`RStudio`](https://rstudio.com/products/rstudio/download/#download). 

+ Install `Nimble` following [these guidelines](https://r-nimble.org/download). Then run the following code in `R`. If that runs without error, you're all set.

    ```{r eval = FALSE, echo = TRUE}
    library(nimble)
    code <- nimbleCode({
    y ~ dnorm(0,1)
    })
    model <- nimbleModel(code)
    cModel <- compileNimble(model)
    ```
    
+ Install the following `R` packages: `tidyverse`, `MCMCvis`, `here` and `nimbleEcology`. You can install them all at once by running the following code in `R`:

    ```{r eval = FALSE, echo = TRUE}
    install.packages(c("tidyverse", "MCMCvis", "here", "nimbleEcology"))
    ```


### Reuse {.appendix}

Text and figures are licensed under Creative Commons Attribution [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/). Any computer code (R, HTML, CSS, etc.) in slides and worksheets, including in slide and worksheet sources, is also licensed under [MIT](https://raw.githubusercontent.com/oliviergimenez/NETDEM-workshop-survival-nimble/main/LICENSE.md). 

